Constructing Sailing Match Race Schedules: Round Robin Pairing Lists

### 2015-03-25 paper.tex
Colour in table columns
Reorder a bit

\usepackage{amssymb}
\usepackage[fleqn]{amsmath}
\usepackage{url}
\usepackage{graphicx}
\usepackage{float}
\usepackage{listings}
\usepackage[ruled,vlined]{algorithm2e}
\usepackage{mathtools}
\usepackage[rightcaption]{sidecap}
\usepackage{multicol}
\usepackage{booktabs}
\usepackage{framed}
\usepackage{coffee2}
\usepackage{tikz}

@@

\begin{SCtable}[2.0][tb]
    \begin{tabular}{c@{\hspace{1em}}c@{\hspace{0.5em}}c@{\hspace{0.5em}}c}
        \toprule
        Flight & \multicolumn{3}{c}{Matches} \\ \midrule
        0 & (0,1) & (2,3) & (4,5) \\
        1 & (0,2) & (4,6) & (1,5) \\
        2 & (2,6) & (0,5) & (1,3) \\
        3 & (5,6) & (0,3) & (1,4) \\
        4 & (3,5) & (1,6) & (2,4) \\
        5 & (3,6) & (0,4) & (2,5) \\
        6 & (3,4) & (1,2) & (0,6) \\ \bottomrule
    \end{tabular}
    \caption{A round-robin schedule with 7 skippers, 6 boats and 7 flights.
        Skippers are numbered 0 to 6. Note that the order of skippers within a flight
        is significant, as is position within a match (port or starboard). This
        schedule is the result of stages 1 and 2, and has yet to be renumbered and
        oriented (stages 3 and 4).} \label{tab1}
\end{SCtable}

@@

    \begin{scope}
        \node at (-3.8, 0) {
            \begin{minipage}{4.5cm}
                \centering
                \begin{tabular}{c@{\hspace{1em}}c@{\hspace{0.5em}}c@{\hspace{0.5em}}c}
                    \toprule
                    Flight & \multicolumn{3}{c}{Matches} \\ \midrule
                    0 & (0,1) & (2,3) & \textbf{(4,5)} \\
                    1 & (0,2) & (4,6) & \textbf{(1,5)} \\
                    2 & (2,6) & \textbf{(0,5)} & (1,3) \\
                    3 & \textbf{(5,6)} & (0,3) & (1,4) \\
                    4 & \textbf{(3,5)} & (1,6) & (2,4) \\
                    5 & (3,6) & (0,4) & \textbf{(2,5)} \\
                    6 & (3,4) & (1,2) & (0,6) \\ \bottomrule
                \end{tabular}
            \end{minipage}
        };
    \end{scope}

@@

Figure \ref{schedChanges} gives a pictorial view of the model, using the 7
skipper and 6 boat problem. On the right we have the 7 skippers with their
states and time slots. Again, top right, we give the schedule actually
produced.  Middle left we have the $\match$ array and at the bottom the
$\timeVar$ array. Above the $match$ array we have the $\modMatch$ array. The
yellow arrows show the channeling between parts of the model.

@@

The decision variables are $\timeVar[{0}]$ to $\timeVar[{t-1}]$, i.e.\ for each
time slot we decide what match takes place. A symmetry break is made at the top
of search by forcing the first round to contain the matches $(0,1), (2,3), \nldots$,
i.e.\ $\forall_{i \in [0 \nldots m-1]} ~ \match[{2i,2i+1}] = i$. The schedule
presented has 6 boat changes: there are no boat changes in flight 0 (first
flight), flight 1 skipper 6 has a boat change, flight 2 skipper 3 has a boat
change, flight 3 it's skipper 4, flight 4 skipper 6, flight 5 skipper 0 and
last flight skipper 1.

>>>>

\usepackage{amssymb}
\usepackage[fleqn]{amsmath}
\usepackage{url}
\usepackage{graphicx}
\usepackage{float}
\usepackage{listings}
\usepackage[ruled,vlined]{algorithm2e}
\usepackage{mathtools}
\usepackage[rightcaption]{sidecap}
\usepackage{multicol}
\usepackage{colortbl}
\usepackage{booktabs}
\usepackage{framed}
\usepackage{coffee2}
\usepackage{tikz}

@@

\begin{SCtable}[2.0][tb]
    \setlength{\tabcolsep}{3pt}
    \begin{tabular}{cccc}
        \toprule
        Flight & \multicolumn{3}{c}{Matches} \\ \midrule
        0 & (0,1) & (2,3) & (4,5) \\
        1 & (0,2) & (4,6) & (1,5) \\
        2 & (2,6) & (0,5) & (1,3) \\
        3 & (5,6) & (0,3) & (1,4) \\
        4 & (3,5) & (1,6) & (2,4) \\
        5 & (3,6) & (0,4) & (2,5) \\
        6 & (3,4) & (1,2) & (0,6) \\ \bottomrule
    \end{tabular}
    \caption{A round-robin schedule with 7 skippers, 6 boats and 7 flights.
        Skippers are numbered 0 to 6. Note that the order of skippers within a flight
        is significant, as is position within a match (port or starboard). This
        schedule is the result of stages 1 and 2, and has yet to be renumbered and
        oriented (stages 3 and 4).} \label{tab1}
\end{SCtable}

@@

    \begin{scope}
        \node at (-3.8, 0) {
            \begin{minipage}{4.5cm}
                \centering
                \setlength{\tabcolsep}{3pt}
                \setlength{\aboverulesep}{0pt}
                \setlength{\belowrulesep}{0pt}
                \setlength{\extrarowheight}{.75ex}
                \begin{tabular}{c>{\columncolor{uofgcobalt}}c>{\columncolor{uofgsunshine}}c>{\columncolor{uofglawn}}c}
                    \toprule
                    Flight & \multicolumn{3}{c}{Matches} \\[2pt] \midrule
                    0 & (0,1) & (2,3) & \textbf{(4,5)} \\
                    1 & (0,2) & (4,6) & \textbf{(1,5)} \\
                    2 & (2,6) & \textbf{(0,5)} & (1,3) \\
                    3 & \textbf{(5,6)} & (0,3) & (1,4) \\
                    4 & \textbf{(3,5)} & (1,6) & (2,4) \\
                    5 & (3,6) & (0,4) & \textbf{(2,5)} \\
                    6 & (3,4) & (1,2) & (0,6) \\ \bottomrule
                \end{tabular}
            \end{minipage}
        };
    \end{scope}

@@

Figure \ref{schedChanges} gives a pictorial view of the entire model, using the
7 skipper and 6 boat problem. On the right we have the 7 skippers with their
states and time slots. Again, top right, we give the schedule actually
produced.  Middle left we have the $\match$ array and at the bottom the
$\timeVar$ array. Above the $match$ array we have the $\modMatch$ array. The
yellow arrows show the channeling between parts of the model.

The schedule presented has 6 boat changes: there are no boat changes in flight
0 (first flight), in flight 1 skipper 6 has a boat change, in flight 2 skipper
3 has a boat change, in flight 3 skipper 4, in flight 4 skipper 6, in flight 5
skipper 0, and flight 6 skipper 1.

\paragraph{Decision variables:} The decision variables are $\timeVar[{0}]$ to
$\timeVar[{t-1}]$, i.e.\ for each time slot we decide what match takes place. A
symmetry break is made at the top of search by forcing the first round to
contain the matches $(0,1), (2,3), \nldots$, i.e.\ $\forall i \in \{0 \nldots
{m-1}\} : \match[{2i, 2i+1}] = i$.

@@
